---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)
library(tidyverse)
```


```{css}
@import url('https://fonts.googleapis.com/css2?family=Winky+Sans:ital,wght@0,300..900;1,300..900&display=swap');

@import url('https://fonts.googleapis.com/css2?family=Quicksand:wght@300..700&family=Winky+Sans:ital,wght@1,800&display=swap');


h2 {
  color: #5351B8;
  font-family: "Winky Sans", sans-serif;
  font-weight: 600;
  font-style: italic;
  font-size: 30px;
}

h3 {
  color: #4B558D;
  font-family: "Winky Sans", sans-serif;
  font-weight: 600;
  font-style: italic;
  font-size: 20px;
}

body {
  color: black;
  font-family: "Quicksand", sans-serif;
  font-weight: 400;
  font-style: normal;
  font-size: 15px;
}
```



## Music Listening Trends

 This report shows insights into people's music listening habits based on the responses to my survey.

 
 The main things I focused on are:

- **What people are doing when listening to music**
- **What genre they are listening to**
- **Impact of music on productivity**



```{r data}
# Read data directly from the URL into logged_data
logged_data <- 
  read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vTZo3MZYeuFlH1P7LbRwDMO-ZsiqvvOKQAxpHsQDlcLEzSFPJne-v1FoHd_sZ-AnDP98sPSVrWT_5rN/pub?gid=1829976472&single=true&output=csv")


# Rename the variables in logged_data and create latest_data
latest_data <- logged_data %>%
  rename(
    activity = 2,
    genre = 3,
    mood = 4,
    productivity = 5,
    device = 6,
    hours = 7,
  ) %>%
  select(activity, genre, mood, productivity, device, hours) 
```


## Bar Charts

### 1. Most Common Activities While Listening to Music

```{r barchart1}
# Count occurrences of each activity
activity_counts <- latest_data %>%
  count(activity) %>%
  arrange(desc(n))

# Bar chart: activities
ggplot(activity_counts, aes(x = reorder(activity, -n), y = n)) +
  geom_bar(stat = "identity", fill = "#8895CE") +
  labs(
    x = "Activity",
    y = "Count"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```



### 2. Most Commonly Listened Music Genres During the Activity

```{r barchart2}
# Bar chart: Music Genres
genre_counts <- latest_data %>%
  count(genre) %>%
  arrange(desc(n))

ggplot(genre_counts, aes(x = reorder(genre, -n), y = n)) +
  geom_bar(stat = "identity", fill = "#707BAE") +
  labs(
    x = "Genre",
    y = "Count"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```



### 3. Impact of Music on Productivity

```{r barchart3}
# Bar chart: Productivity impact of music
ggplot(latest_data, aes(x = productivity)) +
  geom_bar(fill = "#9170B0") +
  labs(
    x = "Productivity Score (1-10)",
    y = "Count"
  ) +
  theme_minimal()

```



## Summary Values

```{r summaries}
# Most common activity
most_common_activity <- names(which.max(table(latest_data$activity)))
# Most common genre
most_common_genre <- names(which.max(table(latest_data$genre)))
# Most common device
most_used_device <- latest_data %>% count(device, sort = TRUE) %>% slice(1) %>% pull(device)
# average productivity
avg_productivity <- round(mean(latest_data$productivity), 1)
# average hours
avg_hours <- round(mean(latest_data$hours, na.rm = TRUE), 1)

# Dynamic Comments
comment1 <- paste0("The most frequent activity while listening to music is ", most_common_activity, ".")
comment2 <- paste0("The genre that was mentioned the most is ", most_common_genre, ".")
comment3 <- paste0("The average score respondents gave on how music helps their productivity is ", avg_productivity, ".")
comment4 <- paste("On average, respondents listen to music for", avg_hours, "hours per day, and the most common device used to listen to music is", most_used_device, ".")
```


- I collected responses from `r nrow(latest_data)` participants.
- `r comment1`
- `r comment2`
- `r comment3`
- `r comment4`

